### 2021-08-08 manuscript/manuscript-speed-accuracy.tex
Updated README. Re-compiled manuscript & supplementary materials.

\usepackage{float}
\usepackage{graphicx}
\usepackage{caption}
\usepackage[hyphens]{url}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{stmaryrd}
\usepackage{todonotes}
\usepackage{maori}
\graphicspath{{../figures/}}
\setlength{\abovecaptionskip}{15pt plus 3pt minus 2pt}

@@

Data on the
number of updates to software tools from GitHub such as the number of versions,
commits and contributors was significantly correlated with 
software accuracy (respective Spearman’s rhos = {\color{black}0.15, 0.22, 0.21,} and respective Benjamini \& Hochberg corrected P-values = {\color{black}0.029, 0.042, 0.063}), Figure~\ref{fig:allfactors}B. 
The significance if these features was further confirmed with a permutation test (Figure~\ref{fig:allfactors}B).
These features were not correlated with speed however (see Figure~\ref{fig:allfactors}A \& Supplementary Figure ????).
We also found that reputation metrics such as citations, author and journal H-indices, and the age
of tools were generally \textbf{not} correlated with either tool
accuracy or speed (Figure~\ref{fig:allfactors}A\&B). 
%The strongest
%association was between accuracy and the relative
%number of citations (Spearman’s rho = {\color{black}0.092,
%P-value = 0.047}). But the effect size is only just over the
%significance threshold and may be the result of multiple-testing.

>>>>

\usepackage{float}
\usepackage{graphicx}
\usepackage{caption}
\usepackage[hyphens]{url}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{stmaryrd}
\usepackage{todonotes}
\usepackage{maori}
\graphicspath{{../figures/}}
\usepackage{xr}
\externaldocument{supplementary}

\setlength{\abovecaptionskip}{15pt plus 3pt minus 2pt}

@@

Data on the number of updates to software tools from GitHub such as
the number of versions, commits and contributors was significantly
correlated with software accuracy (respective Spearman’s rhos =
{\color{black}0.15, 0.22, 0.21,} and respective Benjamini \& Hochberg
corrected P-values = {\color{black}0.029, 0.042, 0.063}),
Figure~\ref{fig:allfactors}B.  The significance of these features was
further confirmed with a permutation test
(Figure~\ref{fig:allfactors}B).  These features were not correlated
with speed however (see Figure~\ref{fig:allfactors}A \& Supplementary
Figures~\ref{fig:metricPairs} and~\ref{fig:S2}).  We also found that
reputation metrics such as citations, author and journal H-indices,
and the age of tools were generally \textbf{not} correlated with
either tool accuracy or speed (Figure~\ref{fig:allfactors}A\&B).
%The strongest
%association was between accuracy and the relative
%number of citations (Spearman’s rho = {\color{black}0.092,
%P-value = 0.047}). But the effect size is only just over the
%significance threshold and may be the result of multiple-testing.
